Lasso_RCI_Response

### 2024-02-19 Lasso_RCI_Response.Rmd
Anxiety & Depression seperate LASSO

- Table 3: Correlation table?
- supplemental table 1: Full diagnostic breakdown of sample 
  + (co-occuring by Disorder)
```{r}
Vars_FULL <- Mothership_lasso |>
  select( c(
    RESPONDER_FIGS,
    # Demographics
    Age_1,Some_College:Married,White, #Discharge,
    # Treatment info
    IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
    # Disorders
    Anxiety_D, Mood_D, BPD_P, Trauma_D, Other,
    Anxiety_C,Mood_C,BPD_Co_C,Other_C, Substance_C, Trauma_C, No_Co,
    Current_Dx,
    # Pre-Post stuff
    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
    # RDQ
    rdq_coping_change:rdq_wbs_change
  ))
Vars_FULL <- na.omit(Vars_FULL)

# install.packages("ggcorrplot")
library(ggcorrplot)
model.matrix(~0+., data=Vars_FULL) %>% 
  cor(use="pairwise.complete.obs") %>% 
  ggcorrplot(show.diag=FALSE, type="lower", lab=TRUE, lab_size=2)
```

@@

Preparing data for Lasso
\scriptsize
```{r, warning=FALSE, message=FALSE}
library(glmnet)
library(caret)
#Make sure there are no NAs within the dataset
Mothership_lasso <- Mothership_post |>
    filter(
    !is.na(Some_College),
    !is.na(Female),
    !is.na(IPT_track_1),
    !is.na(White),
    !is.na(RESPONDER_FIGS)
  )

# View(Mothership_lasso)

Vars <- Mothership_lasso |>
  select( c(
    RESPONDER_FIGS,
    # Demographics
    Age_1,Some_College:Married,White,
    # Treatment info
    IPT_track_1, Days_complete_1, Days_not_attended_1, 
    # Disorders
    Anxiety_D, Mood_D, BPD_P, Trauma_D, Other,
    Anxiety_C,Mood_C,BPD_Co_C,Other_C, Substance_C, Trauma_C, No_Co,
    Current_Dx,
    # Pre-Post stuff
    CUDOS_pre,CUXOS_pre, 
  ))

@@

```{r, warning=FALSE, message=FALSE}
# View(Mothership_lasso)
# head(Vars)
# sum(is.na(Vars))
Vars_FULL <- Mothership_lasso |>
  select( c(
    RESPONDER_FIGS,
    # Demographics
    Age_1,Some_College:Married,White, #Discharge,
    # Treatment info
    IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
    # Disorders
    Anxiety_D, Mood_D, BPD_P, Trauma_D, Other,
    Anxiety_C,Mood_C,BPD_Co_C,Other_C, Substance_C, Trauma_C, No_Co,
    Current_Dx,
    # Pre-Post stuff
    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
    # RDQ
    rdq_coping_change:rdq_wbs_change
  ))

Vars_FULL <- na.omit(Vars_FULL)
```
# with RDQ
```{r}
# Create Training and testing data
set.seed(123) 
training.samples <- Vars_FULL$RESPONDER_FIGS %>% 
  createDataPartition(p = 0.8, list = FALSE)
train.data  <- Vars_FULL[training.samples, ]
test.data <- Vars_FULL[-training.samples, ]

# Dumy code categorical predictor variables
x <- model.matrix(RESPONDER_FIGS~., train.data)[,-1]
# Convert the outcome (class) to a numerical variable
y <- ifelse(train.data$RESPONDER_FIGS == "Responder", 1, 0)

#Simplified lasso
lasso1 <- glmnet(x, y,family = "binomial", alpha = 1, lambda = NULL)
plot(lasso1, "lambda", label = TRUE)
```

Find coefficients using cv.lasso
```{r}
# Find the best lambda using cross-validation
set.seed(123) 
cv.lasso <- cv.glmnet(x, y, alpha = 1, family = "binomial")

#The exact value of lambda can be viewed as follow:
print(paste0("This is the minimum lambda value: ", round(cv.lasso$lambda.min,5)))

#This value is called lambda.1se.
print(paste0("This is the 1 standard error lambda value: ", round(cv.lasso$lambda.1se,5)))

# Fit the final model on the training data
model <- glmnet(x, y, alpha = 1, family = "binomial",
                lambda = cv.lasso$lambda.min)
# Display regression coefficients
coef(model)
# Make predictions on the test data
x.test <- model.matrix(RESPONDER_FIGS ~., test.data)[,-1]
probabilities <- model %>% predict(newx = x.test)
predicted.classes <- ifelse(probabilities > 0.5, "Responder", "Non-Responder")
# Model accuracy
observed.classes <- test.data$RESPONDER_FIGS
mean(predicted.classes == observed.classes)

#Using lambda.min as the best lambda, gives the following regression coefficients:
coef(cv.lasso, cv.lasso$lambda.min)

#Using lambda.1se as the best lambda, gives the following regression coefficients:
coef(cv.lasso, cv.lasso$lambda.1se)
```

Evaluating if we should use Lasso min or 1SE
```{r}
####  Using Min
# Final model with lambda.min
lasso.model.min <- glmnet(x, y, alpha = 1, family = "binomial",
                      lambda = cv.lasso$lambda.min)

coef(lasso.model.min)
# Make prediction on test data
x.test <- model.matrix(RESPONDER_FIGS ~., test.data)[,-1]
probabilities <- lasso.model.min %>% predict(newx = x.test)
predicted.classes <- ifelse(probabilities > 0.5, "Responder", "Non-Responder")
# Model accuracy
observed.classes <- test.data$RESPONDER_FIGS
Mean.predict.min <- mean(predicted.classes == observed.classes)

#####  using 1se
# Final model with lambda.1se
lasso.model.1se <- glmnet(x, y, alpha = 1, family = "binomial",
                      lambda = cv.lasso$lambda.1se)
coef(lasso.model.1se)
# Make prediction on test data
x.test <- model.matrix(RESPONDER_FIGS ~., test.data)[,-1]
probabilities <- lasso.model.1se %>% predict(newx = x.test)
predicted.classes <- ifelse(probabilities > 0.5, "Responder", "Non-Responder")

# Model accuracy rate
observed.classes <- test.data$RESPONDER_FIGS
Mean.predict.1se <- mean(predicted.classes == observed.classes)

#### full model
# Fit the model
full.model <- glm(RESPONDER_FIGS ~ ., data = train.data, family = "binomial")

# Make predictions
probabilities <- full.model %>% predict(test.data, type = "response")
predicted.classes <- ifelse(probabilities > 0.5, "Responder", "Non-Responder")
# Model accuracy
observed.classes <- test.data$RESPONDER_FIGS
Mean.predict.full.model <- mean(predicted.classes == observed.classes)

predict.df <- data.frame(
  model = c("Min", "1se", "Full"),
  values = c(Mean.predict.min,Mean.predict.1se,Mean.predict.full.model)
)
predict.df
```
plot the lassos
If We want to do lasso in ggplot
https://stackoverflow.com/questions/48978179/plotting-lasso-beta-coefficients

```{r}
##plot the lambda
plot(lasso1, "lambda", label = TRUE)
## Fancy plot
library(lars)
lasso_FULL = lars(x, y, type='lasso', 
              trace=TRUE, normalize=FALSE, intercept=TRUE)
plot(lasso_FULL, xvar='norm', breaks = FALSE, 
     plottype = 'coefficients', omit.zeros = TRUE)

#CV k folds cross validation
plot(cv.lasso)
```

### Final relaxed lasso
Minimum
```{r}
## install.packages("fuzzySim")
library(fuzzySim) ## For FDR adjusted p values
FDR(pvalues = p_values.min)

library(broom)
# https://cran.r-project.org/web/packages/broom/vignettes/broom.html

## min model
  glm_min <-  
      glm(
      #Outcome varaible
        RESPONDER_FIGS ~ 
      # predictors
        Days_not_attended_1 + Anxiety_D + Mood_D + Substance_C + 
        rdq_coping_change + rdq_pmh_change + rdq_func_change + rdq_wbs_change,
      #data
      data = Vars_FULL, 
      # type of regression : logistic = binary / binomial
      family = "binomial")
# Summary of the model
  summary.min      <- summary(glm_min)

  tidy.summary.min <- tidy(glm_min)

# Coefficients
  coefs.min <- abs(coef(glm_min))

# Odds ratio
  OR.min <- exp(coef(glm_min))

# OR 95% CI
  CI.min <- data.frame(exp(confint(glm_min)))

# P values
  p.values.min <- data.frame(cbind(tidy.summary.min$term,tidy.summary.min$p.value))
  # FDR Adjusted P Values
    adj.p.min <- FDR(pvalues = p_values.min)
    ADJ.p.values.min <- data.frame(rbind(adj.p.min$exclude, adj.p.min$select))

# R^2 values  
   R2.min <- performance::r2(glm_min)

# df for Forrest plots
FP.min <- data.frame(cbind(
  Variable = tidy.summary.min$term[2:length(tidy.summary.min$term)],
  OR = OR.min[2:length(OR.min)],
  OR_low  = CI.min[2:length(CI.min$X2.5..),1],
  OR_high = CI.min[2:length(CI.min$X97.5..),2],
  p.values = p.values.min$X2[2:length(p.values.min$X2)]
                    ))

# Left join the FDR adjusted p.value
FP.min <- left_join(FP.min,ADJ.p.values.min, by = join_by(p.values == p.value))
FP.min
```

1se
```{r}
glm_1se <-  
      glm(
      #Outcome varaible
        RESPONDER_FIGS ~ 
      # predictors
        Days_not_attended_1 + rdq_coping_change + rdq_pmh_change + rdq_func_change +
        rdq_wbs_change,
      #data
      data = Vars_FULL, 
      # type of regression : logistic = binary / binomial
      family = "binomial")

summary(glm_1se)

# Summary of the model
  summary.1se      <- summary(glm_1se)

  tidy.summary.1se <- tidy(glm_1se)

# Coefficients
  coefs.1se <- abs(coef(glm_1se))

# Odds ratio
  OR.1se <- exp(coef(glm_1se))

# OR 95% CI
  CI.1se <- data.frame(exp(confint(glm_1se)))

# P values
  p.values.1se <- data.frame(cbind(tidy.summary.1se$term,tidy.summary.1se$p.value))

  # FDR Adjusted P Values
    adj.p.1se <- FDR(pvalues = p.values.1se)
    ADJ.p.values.1se <- data.frame(rbind(adj.p.1se$exclude, adj.p.1se$select))

# R^2 values  
   R2.1se <- performance::r2(glm_1se)

# df for Forrest plots
FP.1se <- data.frame(cbind(
  Variable = tidy.summary.1se$term[2:length(tidy.summary.1se$term)],
  OR = OR.1se[2:length(OR.1se)],
  OR_low  = CI.1se[2:length(CI.1se$X2.5..),1],
  OR_high = CI.1se[2:length(CI.1se$X97.5..),2],
  p.values = p.values.1se$X2[2:length(p.values.1se$X2)]
                    ))

# Left join the FDR adjusted p.value
FP.1se <- left_join(FP.1se,ADJ.p.values.1se, by = join_by(p.values == p.value))
FP.1se
```

# Without RDQ
Evaluating Methods of Assessing “Optimism”  in Regression Models Daniel Thoya1,*, Antony Waititu1, Thomas Magheto1, Antony Ngunyi2 
- chrome-extension://efaidnbmnnnibpcajpcglclefindmkaj/http://article.sciappliedmathematics.com/pdf/ajams-6-4-2.pdf

Validation of prediction models based on lasso regression with multiply imputed data
- https://bmcmedresmethodol.biomedcentral.com/articles/10.1186/1471-2288-14-116#Sec18

Penalized Logistic Regression Essentials in R: Ridge, Lasso and Elastic Net
http://www.sthda.com/english/articles/36-classification-methods-essentials/149-penalized-logistic-regression-essentials-in-r-ridge-lasso-and-elastic-net/

### Lasso regression - set variables
```{r}
# Create Training and testing data
set.seed(123) 
training.samples <- Vars_full$RESPONDER_FIGS %>% 
  createDataPartition(p = 0.8, list = FALSE)
train.data  <- Vars[training.samples, ]
test.data <- Vars[-training.samples, ]

# Dumy code categorical predictor variables
x <- model.matrix(RESPONDER_FIGS~., train.data)[,-1]
# Convert the outcome (class) to a numerical variable
y <- ifelse(train.data$RESPONDER_FIGS == "Responder", 1, 0)

#Simplified lasso
lasso1 <- glmnet(x, y,family = "binomial", alpha = 1, lambda = NULL)

plot(lasso1, "lambda", label = TRUE)
```

Find coefficients using cv.lasso
```{r}
# Find the best lambda using cross-validation
cv.lasso <- cv.glmnet(x, y, alpha = 1, family = "binomial")
# Fit the final model on the training data
model <- glmnet(x, y, alpha = 1, family = "binomial",
                lambda = cv.lasso$lambda.min)
# Display regression coefficients
coef(model)
# Make predictions on the test data
x.test <- model.matrix(RESPONDER_FIGS ~., test.data)[,-1]
probabilities <- model %>% predict(newx = x.test)
predicted.classes <- ifelse(probabilities > 0.5, "Responder", "Non-Responder")
# Model accuracy
observed.classes <- test.data$RESPONDER_FIGS
mean(predicted.classes == observed.classes)

### Compute lasso regression
#Find the optimal value of lambda that minimizes the cross-validation error:
set.seed(123)
cv.lasso <- cv.glmnet(x, y, alpha = 1, family = "binomial")

#The exact value of lambda can be viewed as follow:
cv.lasso$lambda.min

#This value is called lambda.1se.
cv.lasso$lambda.1se

#Using lambda.min as the best lambda, gives the following regression coefficients:
coef(cv.lasso, cv.lasso$lambda.min)

#Using lambda.1se as the best lambda, gives the following regression coefficients:
coef(cv.lasso, cv.lasso$lambda.1se)
```

Evaluating if we should use Lasso min or SE
```{r}
#### Compute the final lasso model:
# Final model with lambda.min
lasso.model.min <- glmnet(x, y, alpha = 1, family = "binomial",
                      lambda = cv.lasso$lambda.min)

coef(lasso.model.min)
# Make prediction on test data
x.test <- model.matrix(RESPONDER_FIGS ~., test.data)[,-1]
probabilities <- lasso.model.min %>% predict(newx = x.test)
predicted.classes <- ifelse(probabilities > 0.5, "Responder", "Non-Responder")
# Model accuracy
observed.classes <- test.data$RESPONDER_FIGS
mean(predicted.classes == observed.classes)

#####  using 1se
# Final model with lambda.1se
lasso.model.1se <- glmnet(x, y, alpha = 1, family = "binomial",
                      lambda = cv.lasso$lambda.1se)

# Make prediction on test data
x.test <- model.matrix(RESPONDER_FIGS ~., test.data)[,-1]
probabilities <- lasso.model.1se %>% predict(newx = x.test)
predicted.classes <- ifelse(probabilities > 0.5, "Responder", "Non-Responder")

# Model accuracy rate
observed.classes <- test.data$RESPONDER_FIGS
mean(predicted.classes == observed.classes)

#### full model
# Fit the model
full.model <- glm(RESPONDER_FIGS ~ ., data = train.data, family = "binomial")

# Make predictions
probabilities <- full.model %>% predict(test.data, type = "response")
predicted.classes <- ifelse(probabilities > 0.5, "Responder", "Non-Responder")
# Model accuracy
observed.classes <- test.data$RESPONDER_FIGS
mean(predicted.classes == observed.classes)
```

Visualizing it
```{r}
library(lars)

lasso5 = lars(x, y, type='lasso', 
              trace=TRUE, normalize=FALSE, intercept=TRUE)

plot(lasso5, xvar='norm', breaks = FALSE, 
     plottype = 'coefficients', omit.zeros = TRUE)
```

### Final relaxed lasso
```{r}
## min model
  glm_1se <-  
      glm(RESPONDER_FIGS ~ 
      Days_complete_1 + Days_not_attended_1,
      data = Vars, family = "binomial")
# Summary of the model
  summary.1se      <- summary(glm_1se)
      library(broom)
          # https://cran.r-project.org/web/packages/broom/vignettes/broom.html
  tidy.summary.1se <- tidy(glm_1se)

# Coefficients
  coefs.1se <- abs(coef(glm_1se))

# Odds ratio
  OR.1se <- exp(coef(glm_1se))

# OR 95% CI
  CI.1se <- data.frame(exp(confint(glm_1se)))

# P values
  p.values.1se <- tidy.summary.1se$p.value

# R^2 values  
   R2.1se <- performance::r2(glm_1se)

# df for Forrest plots

FP.1se <- data.frame(cbind(
  Variable = tidy.summary.1se$term[2:length(tidy.summary.1se$term)],
  OR = OR.1se[2:length(OR.1se)],
  OR_low  = CI.1se[2:length(CI.1se$X2.5..),1],
  OR_high = CI.1se[2:length(CI.1se$X97.5..),2],
  p.values = p.values.1se[2:length(p.values.1se)]
                    ))

FP.1se
```

```{r}
### min model
  glm_min <-  
      glm(RESPONDER_FIGS ~ 
      Age_1 + Some_College + Married + Days_complete_1 + Days_not_attended_1 + 
      Psychotic_D + Co_Substance + Co_Trauma + CUDOS_pre,
      data = Vars, family = "binomial")
# Summary of the model
  summary.min      <- summary(glm_min)
      library(broom)
          # https://cran.r-project.org/web/packages/broom/vignettes/broom.html
  tidy.summary.min <- tidy(glm_min)

# Coefficients
  coefs.min <- abs(coef(glm_min))

>>>>

- Table 3: Correlation table?
- supplemental table 1: Full diagnostic breakdown of sample 
  + (co-occuring by Disorder)
```{r}
Vars_dep <- Mothership_post |>
  select( c(
    Depression_Responder,
    # Demographics
    Age_1,Some_College:Married,White, #Discharge,
    # Treatment info
    IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
    # Disorders
    Anxiety_D, Mood_D, BPD_P, Trauma_D, Other,
    Anxiety_C,Mood_C,BPD_Co_C,Other_C, Substance_C, Trauma_C, No_Co,
    Current_Dx,
    # Pre-Post stuff
    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
    # RDQ
    rdq_coping_change:rdq_wbs_change
  ))

Vars_anx <- Mothership_post |>
  select( c(
    Anxiety_Responder,
    # Demographics
    Age_1,Some_College:Married,White, #Discharge,
    # Treatment info
    IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
    # Disorders
    Anxiety_D, Mood_D, BPD_P, Trauma_D, Other,
    Anxiety_C,Mood_C,BPD_Co_C,Other_C, Substance_C, Trauma_C, No_Co,
    Current_Dx,
    # Pre-Post stuff
    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
    # RDQ
    rdq_coping_change:rdq_wbs_change
  ))

Vars_FULL <- na.omit(Vars_dep)

# install.packages("ggcorrplot")
library(ggcorrplot)
model.matrix(~0+., data=Vars_dep) %>% 
  cor(use="pairwise.complete.obs") %>% 
  ggcorrplot(show.diag=FALSE, type="lower", lab=TRUE, lab_size=2)

model.matrix(~0+., data=Vars_anx) %>% 
  cor(use="pairwise.complete.obs") %>% 
  ggcorrplot(show.diag=FALSE, type="lower", lab=TRUE, lab_size=2)

@@

# Depression Lasso 
Preparing data for lasso - Anxiety
```{r}
Mothership_lasso_dep <- Mothership_post |>
    filter(
    !is.na(Some_College),
    !is.na(Female),
    !is.na(IPT_track_1),
    !is.na(White),
    !is.na(Depression_Responder)
  )

Vars_dep <- Mothership_lasso_dep |>
  select( c(
    Depression_Responder,
    # Demographics
    Age_1,Some_College:Married,White, #Discharge,
    # Treatment info
    IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
    # Disorders
    Anxiety_D, Mood_D, BPD_P, Trauma_D, Other,
    Anxiety_C,Mood_C,BPD_Co_C,Other_C, Substance_C, Trauma_C, No_Co,
    Current_Dx,
    # Pre-Post stuff
    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
    # RDQ
    rdq_coping_change:rdq_wbs_change
  ))

Vars_dep <- na.omit(Vars_dep)

@@

Create test and train data - Depression
```{r}
# Create Training and testing data
set.seed(123) 
training.samples <- Vars_dep$Depression_Responder %>% 
  createDataPartition(p = 0.8, list = FALSE)
train.data  <- Vars_dep[training.samples, ]
test.data <- Vars_dep[-training.samples, ]

# Dumy code categorical predictor variables
x.dep <- model.matrix(Depression_Responder~., train.data)[,-1]
# Convert the outcome (class) to a numerical variable
y.dep <- ifelse(train.data$Depression_Responder == "Responder", 1, 0)

#Simplified lasso
lasso1_dep <- glmnet(x.dep, y.dep,family = "binomial", alpha = 1, lambda = NULL)
plot(lasso1_dep, "lambda", label = TRUE)
```

Find coefficients using cv.lasso- Depression
```{r}
# Find the best lambda using cross-validation
set.seed(123) 
cv.lasso.dep <- cv.glmnet(x.dep, y.dep, alpha = 1, family = "binomial")

#The exact value of lambda can be viewed as follow:
print(paste0("This is the minimum lambda value: ", round(cv.lasso.dep$lambda.min,5)))

#This value is called lambda.1se.
print(paste0("This is the 1 standard error lambda value: ", round(cv.lasso.dep$lambda.1se,5)))

# Fit the final model on the training data
model <- glmnet(x.dep, y.dep, alpha = 1, family = "binomial",
                lambda = cv.lasso.dep$lambda.min)
# Display regression coefficients
coef(model)
# Make predictions on the test data
x.test <- model.matrix(Depression_Responder ~., test.data)[,-1]
probabilities <- model %>% predict(newx = x.test)
predicted.classes <- ifelse(probabilities > 0.5, "Responder", "Non-Responder")
# Model accuracy
observed.classes <- test.data$Depression_Responder
mean(predicted.classes == observed.classes)

#Using lambda.min as the best lambda, gives the following regression coefficients:
coef(cv.lasso.dep, cv.lasso.dep$lambda.min)

#Using lambda.1se as the best lambda, gives the following regression coefficients:
coef(cv.lasso.dep, cv.lasso.dep$lambda.1se)
```

Evaluating if we should use Lasso min or 1SE- Depression
```{r}
####  Using Min
# Final model with lambda.min
lasso.model.min.dep <- glmnet(x.dep, y.dep, alpha = 1, family = "binomial",
                      lambda = cv.lasso$lambda.min)

coef(lasso.model.min.dep)
# Make prediction on test data
x.test <- model.matrix(Depression_Responder ~., test.data)[,-1]
probabilities <- lasso.model.min.dep %>% predict(newx = x.test)
predicted.classes <- ifelse(probabilities > 0.5, "Responder", "Non-Responder")
# Model accuracy
observed.classes <- test.data$Depression_Responder
Mean.predict.min.dep <- mean(predicted.classes == observed.classes)

#####  using 1se
# Final model with lambda.1se
lasso.model.1se.dep <- glmnet(x.dep, y.dep, alpha = 1, family = "binomial",
                      lambda = cv.lasso$lambda.1se)
coef(lasso.model.1se.dep)
# Make prediction on test data
x.test <- model.matrix(Depression_Responder ~., test.data)[,-1]
probabilities <- lasso.model.1se.dep %>% predict(newx = x.test)
predicted.classes <- ifelse(probabilities > 0.5, "Responder", "Non-Responder")

# Model accuracy rate
observed.classes <- test.data$Depression_Responder
Mean.predict.1se.dep <- mean(predicted.classes == observed.classes)

#### full model
# Fit the model
full.model.dep <- glm(Depression_Responder ~ ., data = train.data, family = "binomial")

# Make predictions
probabilities <- full.model %>% predict(test.data, type = "response")
predicted.classes <- ifelse(probabilities > 0.5, "Responder", "Non-Responder")
# Model accuracy
observed.classes <- test.data$Depression_Responder
Mean.predict.full.model.dep <- mean(predicted.classes == observed.classes)

predict.df <- data.frame(
  model = c("Min", "1se", "Full"),
  values = c(Mean.predict.min.dep,Mean.predict.1se.dep,Mean.predict.full.model.dep)
)
predict.df
```

plot the lassos- Depression
If We want to do lasso in ggplot
https://stackoverflow.com/questions/48978179/plotting-lasso-beta-coefficients
```{r}
##plot the lambda
plot(lasso1_dep, "lambda", label = TRUE)
## Fancy plot
library(lars)
lasso_FULL_dep = lars(x.dep, y.dep, type='lasso', 
              trace=TRUE, normalize=FALSE, intercept=TRUE)
plot(lasso_FULL_dep, xvar='norm', breaks = FALSE, 
     plottype = 'coefficients', omit.zeros = TRUE)

#CV k folds cross validation
plot(cv.lasso.dep)
```

### Final relaxed lasso- Depression
Minimum- 
```{r}
## install.packages("fuzzySim")
library(fuzzySim) ## For FDR adjusted p values
library(broom) # for tidy regression output

## min model
  glm_min_dep <-  
      glm(
      #Outcome varaible
        Depression_Responder ~ 
      # predictors
        Married + Days_not_attended_1 + Mood_D + Anxiety_C + Substance_C +
        CUDOS_pre + CUXOS_pre + rdq_coping_change + rdq_pmh_change + 
        rdq_func_change,
      #data
      data = Vars_dep, 
      # type of regression : logistic = binary / binomial
      family = "binomial")
# Summary of the model
  summary.min.dep      <- summary(glm_min_dep)

  tidy.summary.min.dep <- tidy(glm_min_dep)
tidy.summary.min
# Coefficients
  coefs.min.dep <- abs(coef(glm_min_dep))

# Odds ratio
  OR.min.dep <- exp(coef(glm_min_dep))

# OR 95% CI
  CI.min.dep <- data.frame(exp(confint(glm_min_dep)))

# P values
  p.values.min.dep <- data.frame(cbind(tidy.summary.min.dep$term,tidy.summary.min.dep$p.value))
  # FDR Adjusted P Values
    adj.p.min.dep <- FDR(pvalues = p.values.min.dep)
    ADJ.p.values.min.dep <- data.frame(rbind(adj.p.min.dep$exclude, adj.p.min.dep$select))

# R^2 values  
   R2.min.dep <- performance::r2(glm_min_dep)

# df for Forrest plots
FP.min.dep <- data.frame(cbind(
  Variable = tidy.summary.min.dep$term[2:length(tidy.summary.min.dep$term)],
  OR = OR.min.dep [2:length(OR.min.dep)],
  OR_low  = CI.min.dep [2:length(CI.min.dep$X2.5..),1],
  OR_high = CI.min.dep [2:length(CI.min.dep$X97.5..),2],
  p.values = p.values.min.dep $X2[2:length(p.values.min.dep$X2)]
                    ))

# Left join the FDR adjusted p.value
FP.min.dep <- left_join(FP.min.dep,ADJ.p.values.min.dep, by = join_by(p.values == p.value))
FP.min.dep
```
1se -
```{r}

## 1se model
  glm_1se_dep <-  
      glm(
      #Outcome varaible
        Depression_Responder ~ 
      # predictors
        rdq_coping_change + rdq_pmh_change + rdq_func_change + rdq_wbs_change,
      #data
      data = Vars_dep, 
      # type of regression : logistic = binary / binomial
      family = "binomial")
# Summary of the model
  summary.1se.dep      <- summary(glm_1se_dep)

  tidy.summary.1se.dep <- tidy(glm_1se_dep)
  tidy.summary.1se.dep
# Coefficients
  coefs.1se.dep <- abs(coef(glm_1se_dep))

# Odds ratio
  OR.1se.dep <- exp(coef(glm_1se_dep))

# OR 95% CI
  CI.1se.dep <- data.frame(exp(confint(glm_1se_dep)))

# P values
  p.values.1se.dep <- data.frame(cbind(tidy.summary.1se.dep$term,tidy.summary.1se.dep$p.value))
  # FDR Adjusted P Values
    adj.p.1se.dep <- FDR(pvalues = p.values.1se.dep)
    ADJ.p.values.1se.dep <- data.frame(rbind(adj.p.1se.dep$exclude, adj.p.1se.dep$select))

# R^2 values  
   R2.1se.dep <- performance::r2(glm_1se_dep)

# df for Forrest plots
FP.1se.dep <- data.frame(cbind(
  Variable = tidy.summary.1se.dep$term[2:length(tidy.summary.1se.dep$term)],
  OR = OR.1se.dep [2:length(OR.1se.dep)],
  OR_low  = CI.1se.dep [2:length(CI.1se.dep$X2.5..),1],
  OR_high = CI.1se.dep [2:length(CI.1se.dep$X97.5..),2],
  p.values = p.values.1se.dep$X2[2:length(p.values.1se.dep$X2)]
                    ))

# Left join the FDR adjusted p.value
FP.1se.dep <- left_join(FP.1se.dep,ADJ.p.values.1se.dep, by = join_by(p.values == p.value))
FP.1se.dep
```

# Anxiety Lasso 
Preparing data for lasso - Anxiety
```{r}
Mothership_lasso_anx <- Mothership_post |>
    filter(
    !is.na(Some_College),
    !is.na(Female),
    !is.na(IPT_track_1),
    !is.na(White),
    !is.na(Anxiety_Responder)
  )

Vars_anx <- Mothership_lasso_anx |>
  select( c(
    Anxiety_Responder,
    # Demographics
    Age_1,Some_College:Married,White, #Discharge,
    # Treatment info
    IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
    # Disorders
    Anxiety_D, Mood_D, BPD_P, Trauma_D, Other,
    Anxiety_C,Mood_C,BPD_Co_C,Other_C, Substance_C, Trauma_C, No_Co,
    Current_Dx,
    # Pre-Post stuff
    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
    # RDQ
    rdq_coping_change:rdq_wbs_change
  ))

Vars_anx <- na.omit(Vars_anx)
```

Create test and train data - ANX
```{r}
# Create Training and testing data
set.seed(123) 
training.samples <- Vars_anx$Anxiety_Responder %>% 
  createDataPartition(p = 0.8, list = FALSE)
train.data  <- Vars_anx[training.samples, ]
test.data <- Vars_anx[-training.samples, ]

# Dumy code categorical predictor variables
x <- model.matrix(Anxiety_Responder~., train.data)[,-1]
# Convert the outcome (class) to a numerical variable
y <- ifelse(train.data$Anxiety_Responder == "Responder", 1, 0)

#Simplified lasso
lasso1_anx <- glmnet(x, y,family = "binomial", alpha = 1, lambda = NULL)
plot(lasso1_anx, "lambda", label = TRUE)
```

Find coefficients using cv.lasso- ANX
```{r}
# Find the best lambda using cross-validation
set.seed(123) 
cv.lasso.anx <- cv.glmnet(x, y, alpha = 1, family = "binomial")

#The exact value of lambda can be viewed as follow:
print(paste0("This is the minimum lambda value: ", round(cv.lasso.anx$lambda.min,5)))

#This value is called lambda.1se.
print(paste0("This is the 1 standard error lambda value: ", round(cv.lasso.anx$lambda.1se,5)))

# Fit the final model on the training data
model <- glmnet(x, y, alpha = 1, family = "binomial",
                lambda = cv.lasso.anx$lambda.min)
# Display regression coefficients
coef(model)
# Make predictions on the test data
x.test <- model.matrix(Anxiety_Responder ~., test.data)[,-1]
probabilities <- model %>% predict(newx = x.test)
predicted.classes <- ifelse(probabilities > 0.5, "Responder", "Non-Responder")
# Model accuracy
observed.classes <- test.data$Anxiety_Responder
mean(predicted.classes == observed.classes)

#Using lambda.min as the best lambda, gives the following regression coefficients:
coef(cv.lasso.anx, cv.lasso.anx$lambda.min)

#Using lambda.1se as the best lambda, gives the following regression coefficients:
coef(cv.lasso.anx, cv.lasso.anx$lambda.1se)
```

Evaluating if we should use Lasso min or 1SE- ANX
```{r}
####  Using Min
# Final model with lambda.min
lasso.model.min.anx <- glmnet(x, y, alpha = 1, family = "binomial",
                      lambda = cv.lasso$lambda.min)

coef(lasso.model.min.anx)
# Make prediction on test data
x.test <- model.matrix(Anxiety_Responder ~., test.data)[,-1]
probabilities <- lasso.model.min.anx %>% predict(newx = x.test)
predicted.classes <- ifelse(probabilities > 0.5, "Responder", "Non-Responder")
# Model accuracy
observed.classes <- test.data$Anxiety_Responder
Mean.predict.min.anx <- mean(predicted.classes == observed.classes)

#####  using 1se
# Final model with lambda.1se
lasso.model.1se.anx <- glmnet(x, y, alpha = 1, family = "binomial",
                      lambda = cv.lasso$lambda.1se)
coef(lasso.model.1se.anx)
# Make prediction on test data
x.test <- model.matrix(Anxiety_Responder ~., test.data)[,-1]
probabilities <- lasso.model.1se.anx %>% predict(newx = x.test)
predicted.classes <- ifelse(probabilities > 0.5, "Responder", "Non-Responder")

# Model accuracy rate
observed.classes <- test.data$Anxiety_Responder
Mean.predict.1se.anx <- mean(predicted.classes == observed.classes)

#### full model
# Fit the model
full.model.anx <- glm(Anxiety_Responder ~ ., data = train.data, family = "binomial")

# Make predictions
probabilities <- full.model %>% predict(test.data, type = "response")
predicted.classes <- ifelse(probabilities > 0.5, "Responder", "Non-Responder")
# Model accuracy
observed.classes <- test.data$Anxiety_Responder
Mean.predict.full.model.anx <- mean(predicted.classes == observed.classes)

predict.df <- data.frame(
  model = c("Min", "1se", "Full"),
  values = c(Mean.predict.min.anx,Mean.predict.1se.anx,Mean.predict.full.model.anx)
)
predict.df
```

plot the lassos- Anx
If We want to do lasso in ggplot
https://stackoverflow.com/questions/48978179/plotting-lasso-beta-coefficients
```{r}
##plot the lambda
plot(lasso1_anx, "lambda", label = TRUE)
## Fancy plot
library(lars)
lasso_FULL_anx = lars(x, y, type='lasso', 
              trace=TRUE, normalize=FALSE, intercept=TRUE)
plot(lasso_FULL_anx, xvar='norm', breaks = FALSE, 
     plottype = 'coefficients', omit.zeros = TRUE)

#CV k folds cross validation
plot(cv.lasso.anx)
```

### Final relaxed lasso- anx
Minimum- 
```{r}
## install.packages("fuzzySim")
library(fuzzySim) ## For FDR adjusted p values
library(broom) # for tidy regression output

## min model
  glm_min_anx <-  
      glm(
      #Outcome varaible
        Anxiety_Responder ~ 
      # predictors
        Some_College + Married + White + Days_complete_1 + Days_not_attended_1 + 
        Anxiety_D + Other + Mood_C + BPD_Co_C + Substance_C + Trauma_C + Current_Dx +
        CUDOS_pre + CUXOS_pre + rdq_coping_change + rdq_pmh_change + rdq_func_change,
      #data
      data = Vars_anx, 
      # type of regression : logistic = binary / binomial
      family = "binomial")
# Summary of the model
  summary.min.anx      <- summary(glm_min_anx)

  tidy.summary.min.anx <- tidy(glm_min_anx)
  tidy.summary.min.anx
# Coefficients
  coefs.min.anx <- abs(coef(glm_min_anx))

# Odds ratio
  OR.min.anx <- exp(coef(glm_min_anx))
